\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage{titling}
\usepackage{babel}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{amsfonts}
\newcommand\mypound{\scalebox{0.8}{\raisebox{0.4ex}{\#}}}

\setlength{\droptitle}{-11em}

\title{\textbf{Homework Problem Set \mypound 3}}


\author{Harvey Mudd College}
\date{January 2020}

\begin{document}

\maketitle

\noindent\large{}Let $R$ be a ring with identity $1\neq0,$ let F be a field, and let x be an indeterminate over F.
\color{red}
\section*{\hspace{-1cm}9.1.2\Large{} \color{black} \normalfont Let $p(x, y, z) = 2x^2y -3xy^3z + 4y^2z^5$ and $q(x, y,z)= 7x^2 + 5x^2 y^3z^4 - 3x^2z^3$ be polynomials in $\mathbb{Z}[x,y,z]$.
\\
\\
   (a) Write each of $p$ and $q$ as a polynomial in x with coefficients in $\mathbb{Z}[x,y]$.
\\ (b) Find the degree of each of $p$ and $q$.
\\ (c) Find the degree of $p$ and $q$ in each of the three variables $x$, $y$ and $z$.
\\ (d) Compute $pq$ and find the degree of $pq$ in each of the three variables $x, y$ and $z$.
\\ (e) Write $pq$ as a polynomial in the variable $z$ with coefficients in $\mathbb{Z}[x,y]$.
\\
\\
2. Repeat the preceding exercise under the assumption that the coefficients of $p$ and $q$ are in
$\mathbb{Z}/3\mathbb{Z}$.
}
\newpage
\color{red}
\section*{\hspace{-1cm}9.1.6\Large{} \color{black} \normalfont Prove that $(x, y)$ is not a principal ideal in $\mathbb{Q}[x,y].$}
         
\newpage

\color{black}
\section*{\hspace{-1cm}9.1.7\Large{} \color{black} \normalfont Prove that a polynomial ring in more than one variable over $R$ is not a Principal Ideal Domain.}

\newpage

\section*{\hspace{-1cm}9.2.1\Large{} \color{black} \normalfont Let $f(x) \in F[x]$ be a polynomial of degree $n \geq 1$ and let bars denote passage to the quotient $F[x]/f(x)$. Prove that for each $\overline{g(x)}$ there is a unique polynomial $g_0(x)$ of degree  $\leq n - 1$ such that $\overline{g(x)} = \overline{g_0(x)}$ (equivalently, the elements $\overline{1}, \overline{x},...,\overline{x^{n-1}}$
are a $basis$ of the vector space $F[x]/((f(x))$ in particular, the dimension of this space is $n$). [Use the Division Algorithm.].}
\newpage
\section*{\hspace{-1cm}9.2.2\Large{} \color{black} \normalfont Let $F$ be a finite field of order $q$ and let $f(x)$ be a polynomial in $F[x]$ of degree $n \geq 1$. Prove that $F[x]/(f(x))$ has $q^n$ elements. [Use the preceding exercise.]}
\newpage
\section*{\hspace{-1cm}9.2.3\Large{} \color{black} \normalfont Let $f(x)$ be a polynomial in $F[x]$. Prove that $F[x]/(f(x))$ is a field if and only if $f(x)$ is irreducible. [Use Proposition 7, Section 8.2.]}
\newpage
\color{red}
\section*{\hspace{-1cm}9.2.4\Large{} \color{black} \normalfont Let $F$ be a finite field. Prove that $F[x]$ contains infinitely many primes. (Note that over an infinite field the polynomials of degree 1 are an infinite set of primes in the ring of polynomials).}
         
\newpage
\color{red}
\section*{\hspace{-1cm}9.2.6\Large{} \color{black} \normalfont Describe (briefly) the ring structure of the following rings:
\begin{center}
    \textbf{(a)} $\mathbb{Z}[x]/(2)$ \hspace{0.3cm} \textbf{(b)} $\mathbb{Z}[x]/(x)$ \hspace{0.3cm} \textbf{(c)} $\mathbb{Z}[x]/(x^2)$ \hspace{0.3cm}
\\
\vspace{0.3cm}
    \textbf{(d)} $\mathbb{Z}[x,y]/(x^2, y^2, 2)$
\end{center}
Show that $\alpha^2 = 0$ or 1 for every $\alpha$ in the last ring and determine those elements with
$\alpha^2 = 0$. Determine the characteristics of each of these rings (cf. Exercise 26, Section 7.3).}
\newpage
\color{black}
\section*{\hspace{-1cm}9.3.3\Large{} \color{black} \normalfont Let $F$ be a field. Prove that the set $R$ of polynomials in $F[x]$ whose coefficient of x is
equal to 0 is a subring of $F[x]$ and that $R$ is not a U.F.D. 
\vspace{0.3cm}
\\ $[$Show that $x^6 = {(x^2)}^3={(x^3)}^2$ gives two distinct factorizations of $x^6$ into irreducibles.$]$}
\end{document}